How One Microtask Affects Another

### 2016-01-04 docs/publications/2015.12_CHI/man.tex
new version of manuscript -- first sheparding iteration

\begin{abstract}
Microtask platforms are becoming commonplace tools for performing human
research, producing gold-standard data, and annotating large datasets.
These platforms connect \textit{requesters}
(researchers or companies) with large populations (crowds) of workers, who 
perform small tasks, typically taking less than five minutes each.
A topic of ongoing research concerns the design of tasks that elicit high
quality annotations.
Here we identify a seemingly banal feature of nearly all crowdsourcing 
workflows that profoundly impacts workers' responses.
Microtask assignments typically consist of a sequence 
of tasks sharing a common format (e.g., circle galaxies in an image). 
Using image-labeling, a canonical microtask format, we 
discover that earlier tasks have a priming effect on the worker, shifting 
the distribution of future responses by 30-50\% 
(total variational distance). 
Specifically, prior tasks influence the content that workers focus on, 
as well as the richness and specialization of responses. 
We call this phenomenon \textit{intertask effects}.
We compare intertask effects to the overt framing, 
effected by stating the requester's research interest, 
and find that intertask effects are on par or stronger.
If uncontrolled, intertask effects could be a source of systematic bias, 
but our results suggest that, with appropriate task design, 
they might be leveraged to hone worker focus and acuity, 
helping to elicit reproducible, expert-level judgments.
Intertask effects are a crucial aspect of human computation that should be
considered in the design of any crowdsourced study.
\end{abstract}

\keywords{Microtask; crowdsourcing; priming; task-design; bias; classifier}

@@

\section{Introduction}
There are many tasks that are trivial for people, but difficult to solve
programmatically.  
Such tasks include tagging and categorizing images,
%\cite{6116320,Zhai2012357}, 
coding and transcribing media,
%\cite{chandler2013breaking,Berinsky2012351,Finnerty2013},%paolacci2010running},
%judging the relevancy or quality of content,
and performing surveys for 
academic or market research purposes (see Table~\ref{table:task_composition} for a listing of task types seen on the Amazon's Mechanical Turk 
microtask platform).
%\cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
Many tasks are ill-defined, in the sense that they do not have
a clear ``correct'' response, and require high-level, qualitative judgment.
Microtask platforms are marketplaces that help fill the gap in current 
computational capabilities, by matching requesters, who need to have such 
tasks completed, with human workers.  Amazon's Mechanical Turk\footnote{\url{mturk.com}}, and 
CrowdFlower\footnote{\url{crowdflower.com}} are two popular microtask 
platforms.

@@

Psychological experiments show that the exposure to stimuli immediately 
before performing a task influences performance, an effect known as 
\textit{priming} \cite{BJOP1796}.
The effect of priming appears to be stronger when the modality of the
prime is the same as the task.
Thus, the typical microtask setup creates conditions in which
the contents of earlier tasks could influence responses to later ones.

We seek to determine if any such effects in fact occur and if so, 
to measure and characterize them.
Certain tasks admit a well-defined notion of ``correct'' and 
``incorrect'' responses.  But many tasks involving qualitative judgment
do not.  Rather than simply characterizing effects on accuracy, we seek
to provide a generalized measure of the extent to which prior tasks
can alter the distribution of responses to a task.  
Measuring the \textit{extent} of the shift in response distribution, is 
substantially harder than simply determining \textit{whether} an effect 
has occurred.  Our first contribution is a statistically grounded method 
for doing so.

To investigate the phenomenon in a
highly generalizable setting, we sought a task that would involve 
qualitative judgment and enable relatively unconstrained responses. 
We also sought a task that would be a typical exemplar of the kinds of
tasks actually seen on microtask platforms (see 
Table~\ref{table:task_composition} for examples).  For this purpose, we 
adopted
image-labeling as a canonical microtask, in which workers provide 
descriptive labels to images using free-text inputs.  Image labeling is
a qualitative task without clearly ``correct'' or ``incorrect'' responses,
and is among the most common kinds of tasks on the major crowdsourcing
platform Amazon's Mechanical Turk (see Table \ref{table:task_composition}).
If task-induced priming arises in our 
setup, it could be expected in a large number of microtasks and 
crowdsourced workflows where workers are called upon to provide qualitative
judgment.

In our experiments, workers label a series of images, one at a time.
Depending on the treatment to which a worker is assigned, we vary the
images in the first five tasks, while keeping those in the last five tasks 
the same.  For example, in one experiment, the first five images shown to
one group of workers contained food, while those shown to the other 
contained (non-food) objects.  The last five images for both
groups contained both food and objects.

@@

As a point of comparison, our experiments included framing treatments, 
in which we altered the framing of microtask assignments, in terms of the 
stated purpose of the task, or by naming the funder.
Remarkably, the effects of prior microtasks themselves,
which are virtually ubiquitous, are on par with, or stronger than, 
overtly framing an assignment.

@@

As our main contributions, we
\begin{itemize}[noitemsep,nolistsep]
  \item{
	derive a method for measuring changes in response distributions;
  }
  \item{measure the influence of initial microtasks on later ones;}
  \item{show this effect is stronger than, or on par with framing;}
  \item{
	show that when completing a series of similar microtasks,
	worker's responses become more specialized and diverse;
  }
\end{itemize}

The rest of the paper is organized as follows.  In the next section, we 
review the relevant prior work.  We then present our method for 
measuring changes to response distributions.
Next we present our experimental results, followed by a discussion 
of interpretations and ramifications for microtask-based and crowdsourced 
work.  We conclude with suggestions for task design and future work.

\section{Prior work}
\subsection{Effects of microtask design on response quality}
% Accuracy, reproducibility, and a controlled task environment are 
% important
Microtask platforms are increasingly used to clean and codify datasets,
administer experiments with human participants, and distribute 
surveys.  Accuracy and replicability are crucial in all of these 
applications.

@@

% Task framing
Workers have other motivations for completing tasks aside from 
remuneration \cite{kazai2013analysis}.  
Researchers have attempted to appeal to
worker's motivation to do work that has a meaningful purpose:
when a task was framed as assisting with medical research,
workers are more likely to participate and completed more tasks, than
when they were not provided any context \cite{chandler2013breaking}.
Providing a meaningful context did not, however, increase the 
\textit{quality} of work.

@@

% effects of task interruption
Perhaps the most similar study to the work we describe here 
investigated the effects of interruptions on task performance
\cite{laseckieffects}.  There, workers 
completed a series of tasks that required them to answer questions about
an illustrated map.  When interruptions were introduced
in the form of either a time delay, or a different task involving a
different map, workers took longer to complete the task which 
followed the interruption.  However this study did not test for
effects on the quality of responses.
%\cite{kreifeldt1981interruption}

Taken together, the prior work suggests that, beyond the design
of tasks themselves, the design of the context of tasks has a major
effect on responses.
However, the potential of earlier tasks to act as primes for later ones 
has not been adequately investigated.

@@

As we have mentioned, workers prefer to perform a series of tasks that
are similar to one another.
Moreover, many 
microtasks involve tasks based on visual and auditory perception 
similar to the kinds used in priming studies.
Thus, in a typical microtask assignment, there are many opportunities for 
priming, the effects of which should be explored.

@@

Determining the strength of intertask effects amounts to measuring a 
distance, or \textit{divergence}, between response distributions.
We will present a method for bounding a kind of divergence known as 
\textit{total variational distance}\footnote{
  Other formulations such as the Kullback-Leibler and 
  Jensen-Shannon divergence can be calculated from the total variational
  distance.
}, which we will henceforth denote by $\theta$.
The value of $\theta$ between two distributions $P$ and $Q$ 
is the fraction under the graph of $P$ that does not overlap with that
under $Q$ (or vice-versa; see Figure~\ref{fig:l1_example}).  
Formally:
\begin{align}
	\theta = \frac{1}{2}\sum_{x \in X} \left| p(x) - q(x) \right|,
	\label{eq:theta}
\end{align}
Where $p(x)$ and $q(x)$ are the respective probabilities 
that a worker submits response $x$, from a set of possible responses 
$\mathcal{X}$, under distributions $P$ and $Q$.
The divergence is constrained to 
$0 \leq \theta \leq 1$ (or from 0 to 100\%).
When $\theta = 100\%$, the distributions do not overlap at all.  
When $\theta = 0\%$, the distributions are identical.
For reference, the distributions plotted in 
Figure~\ref{fig:l1_example}A and B have $\theta=50\%$ and $\theta=30\%$ 
respectively.

\begin{figure}
	\centering
	\includegraphics[scale=1.0]{figs/normal_example.pdf}
	\caption{
	  	Normal distributions exhibiting a total variational distance
		of A) 50\% and B) 30\%.  The total variational distance is 
		the non-overlapping portion of the distributions, e.g. in
		A) it is given by 
		$\theta = a_1 / (a_1 + a_2) = a_3 / (a_2 + a_3)$.
	}
	\label{fig:l1_example}
\end{figure}

@@

However this approach can \textit{drastically} overestimate $\theta$
\cite{val-thesis}.  As an illustrative example,
suppose that we have sampled two sets of 1000 words from \textit{possibly} 
different distributions, and that we wish to estimate the divergence 
between these distributions.  
It turns out that, if both sets of words were actually drawn from 
an identical Zipf distribution\footnote{The 
  Zipf distribution is a common model for word frequencies 
  \cite{powers1998applications,zipf1949human}:
  \begin{align}
	p(x) = \frac{x^{-1}}{\sum_{n=1}^{\infty}x^{-1}},
	\label{eq:zipf}
  \end{align}
  where $p(x)$ is the probability of the $x$th most common word.
}, the naive approach would typically lead one to report 
$\hat{\theta} \approx 65\%$, even though, in reality $\theta = 0\%$
(this can be shown by simulated sampling).

@@

Stated formally, any classifier algorithm, $\mathcal{A}$, that
takes the response, $x$, of a worker, and guesses the 
design that elicited the response (from two possibilities:
$\mathrm{design}_1$ or $\mathrm{design}_2$), will do so with accuracy 
$\eta_\mathcal{A}$, that is bounded according to:
\begin{equation}
	\theta \geq 2\eta_\mathcal{A} - 1,
	\label{eq:sup:l1}
\end{equation}
where $\theta$ is the divergence between the distributions of responses
to $\mathrm{design}_1$ and $\mathrm{design}_2$.

We can establish Inequality~\ref{eq:sup:l1} by considering an
optimal classifier having accuracy $\eta_*$.  
Let us assume that workers are shown 
$\mathrm{design}_1$ or $\mathrm{design}_2$ with equal probability.
If the worker gives the response $x$, it is optimal to guess
that the worker was shown the design most likely to elicit $x$.
In other words, if $p_i(x)$ is the probability that a worker shown 
$\mathrm{design}_i$ responds with $x$, then it is optimal to 
guess that the worker saw $\mathrm{design}_j$, where 
$j = \arg\max_j{p_j(x)}$.

@@

\begin{figure*}
	\centering
	\includegraphics[scale=1.0]{figs/images.jpg}
	\caption{
		Examples of images used in
		initial tasks for the (\textbf{A}) \textit{food} and (\textbf{B}) 
		\textit{objects} treatments of \textit{intertask-food-objects};
		(\textbf{C}) test tasks for \textit{intertask-food-objects} and 
		\textit{frame-food-objects};
		initial tasks for the (\textbf{D}) \textit{food} and (\textbf{E}) 
		\textit{culture} treatments of \textit{intertask-food-culture};
		and (\textbf{F}) test tasks for \textit{intertask-food-culture} and 
		\textit{frame-food-culture}.
	}

\begin{figure}[t]
	\includegraphics[scale=0.75]{figs/theta.pdf}
	\caption{
		Empirical bias, $\theta_\mathrm{NB}$, measured using a naive Bayes 
		classifier, induced in image-labeling tasks, due to workers' 
		exposure to framing and prior tasks.  
		(\textbf{A}) Exposing workers to initial tasks induced more severe
		bias than framing, except when echoed framing was used. 
		(\textbf{B}) As workers proceeded through test tasks, 
		the bias due to initial tasks waned, 
		but remained significant even after five tasks.  
		Standard error bars are shown.
	}
	\label{fig:theta}
\end{figure}

The first experiment we performed consisted of two sub-experiments which
we will call ``intertask'' and ``framing'', because they are respectively
designed to measure intertask and framing effects.  The experiment was 
performed on Amazon's Mechanical Turk (MTurk) using 476 workers.  Workers
could only participate once in a given experiment, and could only 
participate in one of the experiments we present here.

The experiment was conducted using a single HIT\footnote{
  On MTurk, a HIT (or Human Intelligence Task) is the smallest 
  assignable unit of work.  The use of ``Task'' in HIT differs from that
  used here; here labeling a single image is considered to be one ``task'',
  and so a HIT is actually composed of 10 tasks.
}.  Workers who accepted the HIT were randomly assigned to one of the two
sub-experiments.  Both sub-experiments consisted of two treatments, which
we call ``food'' and ``culture'', and workers were also randomly 
assigned to a treatment.  In both treatments of both sub-experiments,
workers were asked to perform ten image-labeling tasks, each of which 
required the worker to assign five descriptive labels to an image.  
In all cases, the last five tasks were 
identical, and were presented in the same order.  
These last five tasks constituted the ``test tasks'', whose distribution
of responses could admit intertask or framing effects.

In the intertask sub-experiment, we varied the first five tasks given to 
workers based on the treatment.  Workers assigned to the ``food'' 
treatment were shown images of food, while workers assigned to the 
``culture'' treatment were shown other kinds of cultural depictions, such
as dance, sport, and music\footnote{We do not assert that cultural 
practices can be cleanly separated into food-related and non-food related 
ones; that is not necessary for our analysis.}.  
However, within a given treatment, workers were shown the same images in
the same order.  As mentioned, workers 
from both treatments then performed the same five test tasks.  The test
tasks consisted of images depicting meals of diverse ethnic origin.
From the perspective of the worker, there was no distinction between the 
initial and test tasks.

In the framing sub-experiment, we did not vary the initial tasks, but 
instead, introduced a \textit{framing slide} before the tasks.  
Depending on the treatment, the framing slide read 
``This research is proudly funded by The National Foundation for 
Nutritional Awareness'', or ``\ldots by the Global Foundation for the 
Recognition of Cultures''.  The intention here was to frame the task by
providing the name of a (fictitious) funder, and using names that
invite the worker to focus on different aspects of the image content.  
As already mentioned, the test tasks consisted of images depicting meals 
of diverse ethnic origin.

@@

\paragraph{Existence of intertask and framing effects.} 
Looking at the frequencies with which workers use words, we tested for
heterogeneity between the two treatments of each sub-experiment.
For the intertask sub-experiment, we found the distribution of responses 
for the two treatments differed significantly ($p=?$), 
demonstrating that intertask effects do exist.  However, we did not find 
significant effects due to framing, however (by $\chi^2$ test, $p=0.29$) 
(Figure~\ref{fig:theta}A).

Testing for heterogeneity of word-frequencies was based on 
Pearson's $\chi^2$ test with Yates' correction.
In linguistics applications, the use of a $\chi^2$ to test for 
heterogeneity between corpora has been called
into question, because there is frequently heterogeneity \textit{within}
a given corpus \cite{kilgarriff1996comparing}.
This occurs because certain documents in a corpus will regard certain 
topics, leading to bursty word usage.  While our setup is substantially
remote from the applications for which this concern was raised, 
one could argue that the responses to a given treatment
constitute a ``corpus'', and the responses of a given worker to a 
``document''.
To address this concern, we randomly split responses to given treatment
into two sets, and tested for hetererogeneity between the sets.
In all cases, we failed to find heterogeneity \textit{within} a given 
treatment (with $p > 0.3$ for all treatments and $p > 0.8$ for most).
These results hold for Experiment 2 as well, to be discussed later.
Thus, the heterogeneity we observed \textit{between} treatments is 
meaningful.

\paragraph{Strength of intertask and framing effects.}
Having affirmed the \textit{existence} of intertask effects, we sought to
measure the strength of the effect, i.e. $\theta$.
To measure $\theta$ we created a naive Bayes classifier based on a 
multinomial distribution over the word frequencies in worker's labels, 
and measured it's accuracy using leave-one-out cross-validation.  
We chose the naive Bayes
classifier for three reasons.  First, it performs well even when the 
number of features is large compared to the number of training examples
\cite{bickel2004,hastie2009elements}.  
Second, there are no hyperparameters to 
optimize, which eliminates the need to partition the response data into
dev and test sets.
Third, the conditional independence assumption, normally 
undertaken for pragmatic reasons \cite{Zhang2004562}, 
is probably a mild in 
relation to image labels, since they are likely to be less dependent
on one another than in a coherent passage of text.  We repeated our
analysis using a support vector machine and found very similar results.

To produce word frequency features, worker's labels were split on white
space and punctuation, and the resulting tokens were spell-corrected based
on edit-distance to a dictionary of words, followed by stop-word removal
and lemmatization.  The spelling correction
dictionary was compiled from a combination of WordNet 
\cite{felbaum1998wordnet} and words
collected by crawling the World Food section of \url{allrecipes.com}.

Based on the performance of the classifier, intertask effects generated
51.3\% total variational distance (Figure~\ref{fig:theta}A).  
Visualy comparing two word frequency distributions is difficult, but 
Figure~\ref{fig:l1_example} provides an example of distributions having 
$\theta = 50\%$.  In contrast to intertask effects, the effect due to 
framing, was not significantly different from zero 
(Figure~\ref{fig:theta}A).
And so, the effect framing was weaker than that due to prior tasks 
($p=7.6\times 10^{-7}$)\footnote{To compare bias
  due to framing and intertask effects, we approximated the distribution
  of correct classifications as a normal distribution, and performed
a (two-tailed) two-proportion $z$-test.}.
In other words, the \textit{microtasks themselves}
had a stronger effect than framing.

>>>>

\begin{abstract}
Microtask platforms are becoming commonplace tools for performing human
research, producing gold-standard data, and annotating large datasets.
These platforms connect \textit{requesters}
(researchers or companies) with large populations (crowds) of workers, who 
perform small tasks, typically taking less than five minutes each.
A topic of ongoing research concerns the design of tasks that elicit high
quality annotations.
Here we identify a seemingly banal feature of nearly all crowdsourcing 
workflows that profoundly impacts workers' responses.
Microtask assignments typically consist of a sequence 
of tasks sharing a common format (e.g., circle galaxies in an image). 
Using image-labeling, a canonical microtask format, we 
show that earlier tasks can have a strong influence on responses to later 
tasks, shifting the distribution of future responses by 30-50\% 
(total variational distance). 
Specifically, prior tasks influence the content that workers focus on, 
as well as the richness and specialization of responses. 
We call this phenomenon \textit{intertask effects}.
We compare intertask effects to framing, effected by stating the 
requester's research interest, and find that intertask effects are on 
par or stronger.
If uncontrolled, intertask effects could be a source of systematic bias, 
but our results suggest that, with appropriate task design, 
they might be leveraged to hone worker focus and acuity, 
helping to elicit reproducible, expert-level judgments.
Intertask effects are a crucial aspect of human computation that should be
considered in the design of any crowdsourced study.
\end{abstract}

\keywords{Microtask; crowdsourcing; priming; framing; task-design; bias; classifier}

@@

\section{Introduction}
There are many tasks that are trivial for people, but difficult to solve
programmatically.  
Such tasks include tagging and categorizing images,
%\cite{6116320,Zhai2012357}, 
coding and transcribing media,
%\cite{chandler2013breaking,Berinsky2012351,Finnerty2013},%paolacci2010running},
%judging the relevancy or quality of content,
and performing surveys for 
academic or market research purposes (see Table~\ref{table:task_composition} for a listing of task types seen on the Amazon's Mechanical Turk 
microtask platform).
%\cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
Many tasks are ill-defined, in the sense that they do not have
a clear ``correct'' response, and require high-level, qualitative judgment.
Microtask platforms are marketplaces that help fill the gap in current 
computational capabilities, by matching requesters, who need to have such 
tasks completed, with human workers.  Amazon's Mechanical Turk (MTurk)\footnote{\url{mturk.com}}, and 
CrowdFlower\footnote{\url{crowdflower.com}} are two popular microtask 
platforms.

@@

Psychological experiments show that the exposure to stimuli immediately 
before performing a task influences performance, an effect known as 
\textit{priming} \cite{BJOP1796}.
The effect of priming appears to be stronger when the modality of the
prime is the same as the task.
Thus, for the typical microtask worker, who does many similar tasks in
quick succession, there is a potential for earlier tasks to influence
later ones, via priming or other mechanisms.

We seek to determine if any such effects in fact occur and if so, 
to measure and characterize them.
Certain tasks admit a well-defined notion of ``correct'' and 
``incorrect'' responses.  But many tasks involving qualitative judgment
do not.  So, rather than simply characterizing effects on accuracy, we seek
to provide a generalized measure of the extent to which prior tasks
can alter the distribution of responses to later tasks.  
Measuring the \textit{extent} of the shift in a distribution of responses 
is substantially harder than simply determining \textit{whether} an effect 
has occurred.  Our first contribution is a statistically grounded method 
for doing so.

To investigate the phenomenon in a
highly generalizable setting, we sought a task that would involve 
qualitative judgment and enable relatively unconstrained responses. 
We also sought a task that would be a typical exemplar of the kinds of
tasks actually seen on microtask platforms (see 
Table~\ref{table:task_composition} for examples).  For this purpose, we 
adopted
image-labeling as a canonical microtask, a task in which workers provide 
descriptive labels to images using free-text inputs.  Image labeling is
a qualitative task without clearly ``correct'' or ``incorrect'' responses,
and is among the most common kinds of tasks on MTurk 
(see Table \ref{table:task_composition}).
If task-induced priming arises in our 
setup, it could be expected in a large number of microtasks and 
crowdsourced workflows where workers are called upon to provide qualitative
judgment.

In our experiments, workers label a series of images, one at a time.
Depending on the treatment to which a worker is assigned, we vary the
images in the first five tasks, while keeping those in the last five tasks 
the same.  For example, in one experiment, the first five images shown to
one group of workers contain food, while those shown to the other 
contain (non-food) objects.  The last five images for both
groups contain both food and objects.

@@

As a point of comparison, we also conducted framing experiments, 
in which we altered the framing of microtask assignments, in terms of the 
stated purpose of the task, or by naming the funder.
Remarkably, the effects of prior microtasks,
which are virtually ubiquitous, are on par with, or stronger than, 
the effects of overtly framing an assignment.

@@

As our main contributions, we
\begin{itemize}[noitemsep,nolistsep]
  \item{
	derive a method for measuring changes in response distributions;
  }
  \item{measure the strength of intertask effects;}
  \item{show that intertask effects are stronger than,
	or on par with framing;}
  \item{
	show that when completing a series of similar microtasks,
	worker's responses become more specialized and diverse;
  }
\end{itemize}

The rest of the paper is organized as follows.  In the next section, we 
review the relevant prior work.  We then present our method for 
measuring changes to response distributions.
Next we present our first experiment which measures intertask effects and
compares them to framing. We then describe a second experiment which 
extends these results, addressing questions raised by the first experiment.
We conclude by discussing interpretations and ramifications, suggesting
a possible mechanism for intertask effects based on priming, and
describing directions for future work.

\pagebreak
\section{Prior work}
\subsection{Effects of microtask design on response quality}
% Accuracy, reproducibility, and a controlled task environment are 
% important
Microtask platforms are increasingly used to clean and codify datasets,
administer experiments with human participants, and distribute 
surveys.  Accuracy and replicability are crucial in all of these 
applications.

@@

% Task framing
Workers have other motivations for completing tasks aside from 
remuneration \cite{kazai2013analysis}.  
Researchers have attempted to appeal to
worker's motivation to do work that has a meaningful purpose:
when a task was framed as assisting with medical research,
workers were more likely to participate and completed more tasks, than
when they were not provided any context \cite{chandler2013breaking}.
Providing a meaningful context did not, however, increase the 
\textit{quality} of work.

@@

% effects of task interruption
Other work investigated the effects of interruptions on task performance
\cite{laseckieffects}.  There, workers 
completed a series of tasks that required them to answer questions about
an illustrated map.  When interruptions were introduced
in the form of either a time delay, or a different task involving a
different map, workers took longer to complete the task which 
followed the interruption.  However this study did not test for
effects on the quality of responses.

In a somewhat related vein, other researchers investigated 
the effects of task-switching \cite{yin2014monetary}.  During 
\textit{switch-tasks} (tasks which differ in nature from the immediately 
preceeding task), workers were more inclined to make mistakes, 
and took longer to complete the task.  
However, the reserchers found that by offering a performance-based
bonus, which paid if workers completed the task quickly and correctly,
performance during switch-tasks was both faster and more accurate.

However, long periods of performing the same task can lead to fatigue,
which can be relieved by well placed-interruptions.  A study 
\cite{dai2015and} found that introducing ``micro-diversions'' 
periodically between tasks caused workers to complete more tasks overall, 
and to complete them more quickly.  This was more pronounced for more 
cognitively taxing tasks.

@@

As we have mentioned, workers prefer to perform a series of tasks that
are similar to one another.  Moreover, many 
microtasks involve tasks based on visual and auditory perception 
similar to the kinds used in priming studies.
Thus, in a typical microtask assignment, there are many opportunities for 
priming to arise.

Researchers have begun to explore the potential 
applications of priming in microtask design.  One study found that 
showing workers an image of a laughing baby (so as to stimulate positive
affect), led to better performance in a task requiring creativity
\cite{lewis2011affective}.  This shows that priming effects can play a 
role in microtask design.  The question we seek to answer, however, is 
whether earlier tasks can affect responses to later tasks.

Taken together, the prior work suggests that, beyond the design
of tasks themselves, the design of the context of tasks has a major
effect on responses.  There is reason to believe that, even in a series
of similar tasks, earlier microtasks may influence later ones, such as
through a priming mechanism.  However, no direct investigation of whether 
this phenomenon exists has yet been made, which is the goal of the present 
work.

@@

Determining the strength of intertask effects amounts to measuring a 
distance, or \textit{divergence}, between response distributions.
We will present a method for bounding a kind of divergence known as 
\textit{total variational distance}\footnote{
  Other formulations such as the Kullback-Leibler and 
  Jensen-Shannon divergence can be related to the total variational
  distance.
}, which we will henceforth denote by $\theta$.
The value of $\theta$ between two distributions $P$ and $Q$ 
is the fraction under the graph of $P$ that does not overlap with that
under $Q$ (or vice-versa; see Figure~\ref{fig:l1_example}).  
Formally:
\begin{align}
	\theta = \frac{1}{2}\sum_{x \in X} \left| p(x) - q(x) \right|,
	\label{eq:theta}
\end{align}
Where $p(x)$ and $q(x)$ are the respective probabilities 
that a worker submits response $x$, from a set of possible responses 
$\mathcal{X}$, under distributions $P$ and $Q$.
The divergence is constrained to 
$0 \leq \theta \leq 1$ (or from 0 to 100\%).
When $\theta = 100\%$, the distributions do not overlap at all.  
When $\theta = 0\%$, the distributions are identical.
For reference, the distributions plotted in 
Figure~\ref{fig:l1_example}A and B have $\theta=50\%$ and $\theta=30\%$ 
respectively.

\begin{figure}
	\centering
	\includegraphics[scale=1.0]{figs/normal_example.pdf}
	\caption{
	  	Normal distributions exhibiting a total variational distance
		of (A) 50\% and (B) 30\%.  The total variational distance is 
		the non-overlapping portion of the distributions, e.g. in
		(A) it is given by 
		$\theta = a_1 / (a_1 + a_2) = a_3 / (a_2 + a_3)$.
	}
	\label{fig:l1_example}
\end{figure}

@@

However this approach can \textit{drastically} overestimate $\theta$
\cite{val-thesis}.  As an illustrative example,
suppose that we have sampled two sets of 1000 words from \textit{possibly} 
different distributions, and that we wish to estimate the divergence 
between these distributions.  
It turns out that, if both sets of words were actually drawn from 
an identical Zipf distribution\footnote{The 
  Zipf distribution is a model for word frequencies 
  \cite{powers1998applications,zipf1949human}:
  \begin{align}
	p(x) = \frac{x^{-1}}{\sum_{n=1}^{\infty}x^{-1}},
	\label{eq:zipf}
  \end{align}
  where $p(x)$ is the probability of the $x$th most common word.
}, the naive approach would typically lead one to report 
$\hat{\theta} \approx 65\%$, even though, in reality $\theta = 0\%$
(this can be shown by simulated sampling).

@@

Stated formally, any classifier algorithm, $\mathcal{A}$, that
takes the response, $x$, of a worker, and guesses the 
design that elicited the response (from two possibilities:
$\mathrm{design}_1$ or $\mathrm{design}_2$), will do so with accuracy 
$\eta_\mathcal{A}$, that is bounded according to:
\begin{equation}
	\theta \geq 2\eta_\mathcal{A} - 1,
	\label{eq:sup:l1}
\end{equation}
where $\theta$ is the total variational distance between the 
distributions of responses
to $\mathrm{design}_1$ and $\mathrm{design}_2$.

\begin{figure*}
	\centering
	\includegraphics[scale=0.60]{figs/images.png}
	\caption{
		Examples of images used in
		initial tasks for the (\textbf{A}) \textit{food} and (\textbf{B}) 
		\textit{objects} treatments of \textit{intertask-food-objects};
		(\textbf{C}) test tasks for \textit{intertask-food-objects} and 
		\textit{frame-food-objects};
		initial tasks for the (\textbf{D}) \textit{food} and (\textbf{E}) 
		\textit{culture} treatments of \textit{intertask-food-culture};
		and (\textbf{F}) test tasks for \textit{intertask-food-culture} and 
		\textit{frame-food-culture}.
	}

We can establish Inequality~\ref{eq:sup:l1} by considering an
optimal classifier having accuracy $\eta_*$.  
Let us assume that workers are shown 
$\mathrm{design}_1$ or $\mathrm{design}_2$ with equal probability.
If the worker gives the response $x$, the opitimal classifier must guess
that the worker was shown the design most likely to elicit $x$.
In other words, if $p_i(x)$ is the probability that a worker shown 
$\mathrm{design}_i$ responds with $x$, then it is optimal to 
guess that the worker saw $\mathrm{design}_j$, where 
$j = \arg\max_j{p_j(x)}$.

@@

The first experiment we performed consisted of two sub-experiments which
we will call ``intertask'' and ``framing'', because they are respectively
designed to measure intertask and framing effects.  The experiment was 
performed on MTurk using 476 workers.  Workers
could only participate once in a given experiment, and could only 
participate in one of the experiments we present here.

The experiment was conducted using a single HIT\footnote{
  On MTurk, a HIT (or Human Intelligence Task) is the smallest 
  assignable unit of work.  The use of ``Task'' in HIT differs from that
  used here; here labeling a single image is considered to be one ``task'',
  and so a HIT is actually composed of 10 tasks.
}.  Workers who accepted the HIT were randomly assigned to one of the two
sub-experiments.  Both sub-experiments consisted of two treatments, which
we call ``food'' and ``culture'', and workers were also randomly 
assigned to a treatment.  In both treatments of both sub-experiments,
workers were asked to perform ten image-labeling tasks, each of which 
required the worker to assign five descriptive labels to an image.  
In all cases, the last five tasks were identical among all treatments 
(and across sub-experiments), and were presented in the same order.  
These last five tasks constituted the ``test tasks'', whose distribution
of responses could admit intertask or framing effects.

In the intertask sub-experiment, we varied the first five tasks given to 
workers based on the treatment.  Workers assigned to the ``food'' 
treatment were shown images of food (see Figure~\ref{fig:task}A), 
while workers assigned to the ``culture'' treatment were shown other kinds 
of cultural depictions, such as dance, sport, and 
music\footnote{
  We do not assert that cultural practices can be cleanly separated into 
  food-related and non-food related ones, nor is a strict division 
  necessary for our analysis.
} (see Figure~\ref{fig:task}B).  
However, within a given treatment, workers were shown the same images in
the same order.  As mentioned, workers 
from both treatments then performed the same five test tasks.  The test
tasks consisted of images depicting meals of diverse ethnic origin
(see Figure~\ref{fig:task}C).
From the perspective of the worker, there was no distinction between the 
initial and test tasks.

In the framing sub-experiment, we did not vary the initial tasks, but 
instead, introduced a \textit{framing slide} before the tasks.  
Depending on the treatment, the framing slide read 
``This research is proudly funded by The National Foundation for 
Nutritional Awareness'', or ``\ldots by the Global Foundation for the 
Recognition of Cultures''.  The intention was to frame the task by
providing the name of a (fictitious) funder, while using names that
invite the worker to focus on different aspects of the image content.  
As already mentioned, the test tasks consisted of images depicting meals 
of diverse ethnic origin.

@@

\begin{figure}[t]
    \centering
	\includegraphics[scale=0.85]{figs/theta-exp1.pdf}
	\caption{
	    Lower bound total variational distance ($\theta_\mathrm{NB}$) 
		between responses given
		by workers on test tasks in Experiment 1, when they have been 
		shown different initial tasks (intertask), or been exposed to
		different framing (framing), as determined using naive Bayes 
		classifiers.  Standard error bars are shown.
	}
	\label{fig:theta-exp1}
\end{figure}

\paragraph{Existence of intertask and framing effects.} 
Looking at the frequencies with which workers used words, we tested for
heterogeneity between the two treatments of each sub-experiment.
For the intertask sub-experiment, we found the responses 
for the two treatments differed significantly 
(by $\chi^2$ test, $p<0.001$), 
demonstrating that intertask effects do exist.  However, we did not find 
significant effects due to framing ($p=0.29$) 
(Figure~\ref{fig:theta}A).

Testing for heterogeneity of word-frequencies was based on 
Pearson's $\chi^2$ test with Yates' correction.
In linguistics applications, the use of a $\chi^2$ to test for 
heterogeneity between corpora has been called
into question, because there is frequently heterogeneity \textit{within}
a given corpus \cite{kilgarriff1996comparing}.
This occurs because certain documents in a corpus will regard certain 
topics, leading to bursty word usage.  While our setup is substantially
remote from the applications for which this concern was raised, 
one could argue that the responses to a given treatment
constitute a ``corpus'', and the responses of a given worker to a 
``document''.
To address this concern, we randomly split responses to given treatment
into two sets, and tested for hetererogeneity between the sets.
In all cases, we failed to find heterogeneity \textit{within} a given 
treatment (with $p > 0.3$ for all treatments and $p > 0.8$ for most).
These results hold for Experiment 2, to be discussed later.
Thus, the heterogeneity we observed \textit{between} the intertask 
treatments indicates a meaningful effect.

\paragraph{Strength of intertask and framing effects.}
Having affirmed the \textit{existence} of intertask effects, we sought to
measure their strength, i.e. $\theta$.
To measure $\theta$ we created a naive Bayes classifier based on a 
multinomial distribution over the word frequencies in worker's labels, 
and measured it's accuracy using leave-one-out cross-validation.  
We chose the naive Bayes
classifier for three reasons.  First, it performs well even when the 
number of features is large compared to the number of training examples
\cite{bickel2004,hastie2009elements}.  
Second, there are no hyperparameters to 
optimize, which eliminates the need to partition the response data into
dev and test sets.
Third, the conditional independence assumption, normally 
undertaken for pragmatic reasons \cite{Zhang2004562}, 
is probably mild in 
relation to image labels, since they are likely to be less dependent
on one another than in a coherent passage of text.  We repeated our
analysis using a support vector machine and found very similar results.

To produce word frequency features, worker-submitted labels were split on 
white
space and punctuation, and the resulting tokens were spell-corrected based
on edit-distance to a dictionary of words, followed by stop-word removal
and lemmatization.  The spelling correction
dictionary was compiled from a combination of WordNet 
\cite{felbaum1998wordnet} and words
collected by crawling the World Food section of \url{allrecipes.com}.
